Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.1

### 2020-09-27 expose/main.tex
add info about business connector

Of course, besides being simple and fast, it also has to satisfy requirements of the connector 
and provide its CSS functionalities towards the EA. Typical integration challanges have to be adressed: 
Networks are slow and unreliable, applications have different interfacing requirements or are not 
built to be interfaced at all and possible changes of applications have to be considered.

@@

EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
bricks and data objects.

An integration architecture gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Architecture bricks and data objects 
used in the final form of the integration architecture can be seen as its requirements towards the existing EA.

The integration architecture takes a message based approach by using enterprise integration patterns described
by \cite{integrationPatterns}. This approach aims to solve the previously described challenges in the 
"Problem Statements" section.

The integration architecture gets documented as a component diagram
containing architecture bricks, integration patterns and business connector along with communication 
channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
For each CSS business process, relevant data and instruction flows inside the integration architecture 
are visualized as a sequence diagram.

>>>>

Of course, besides being simple and fast, it also has to enable EA and business connector to access each others 
functionalities according to their requirements.

@@

EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
bricks and data objects, which will make up the enterprise architecture. The requirements of the EA 
regarding the consumption of CSS services will be analyzed. One requirement could e.g. be, that access to 
the \textit{New Address} CSS scenario is required via a web server architecture brick.

CSS scenarios will be used to construct the business connector as a black box of requirements regarding 
access to EA systems and data objects. The black box will also contain interfaces, which provide the CSS 
scenarios. It will not be included, how the business 
connector processes the recieved data, triggers instructions to the EA or implements a service.
The business connector could e.g. consist of the requirements: \textit{access to identities, access to idendity validation, 
access to profile data} and of the interface: \textit{changeIdendityProfileProperty}

An integration architecture gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
the EA and business connector to access each others functionalities according to their requirements considering 
the rigid and heterogenious nature of the EA. Rather technological requirements like scalability and fail safety 
and possible solutions will be evaluated while creating the integration architecture.
Architecture bricks and data objects used in the final form of the 
integration architecture can be seen as its requirements towards the existing EA.

The integration architecture takes a message based approach by using enterprise integration patterns described
by \cite{integrationPatterns}.
The integration architecture gets documented as a component diagram
containing architecture bricks, integration patterns and business connector along with communication 
channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
For each CSS business process, relevant data and instruction flows inside the integration architecture 
are visualized as a sequence diagram.
